%!TEX TS-program = xelatex
\documentclass[]{friggeri-cv}
\addbibresource{bibliography.bib}

\begin{document}
\header{Orhan}{ AYDOGDU}
       {Full Stack Web Developer}


% In the aside, each new line forces a line break
\begin{aside}
  \section{about}
    Istanbul/Turkey
    ~
    \href{mailto:info@orhanaydogdu.com.tr}{info@orhanaydogdu.com.tr}
    \href{tel:+90 541 331 5794}{+90 541 331 5794 (Whatsapp)}
    \href{tel:+7 922 027 4615}{+7 922 027 4615 (Call)}
    \href{https://orhanaydogdu.com.tr?lang=en}{https://orhanaydogdu.com.tr}
    \href{https://www.linkedin.com/in/orhanayd/}{LinkedIn: @orhanayd}
    \href{https://github.com/orhanayd/}{Github: @orhanayd}
  \section{languages}
    Turkish/English
  \section{programming}
    {\color{red} $\varheartsuit$} PHP, JavaScript
    (ES8, Node.JS)
    CSS \& HTML5
\end{aside}

\section{Summary}

5+ years specializing full-stack web developer and cyber security. I love solving problems and fixing problems. I am keen to learn more about computer science and programming technologies required to work with it.

\section{Skills}

PHP, Node.JS, MySQL, MongoDB, PostgreSQL, Redis, Javascript, React.JS / React Native, HTML
HaProxy, Nginx, Kubernetes, Docker, Jenkins, Git

\section{experience}

\begin{entrylist}
  \entry
    {2021}
    {Bisu}
    {Istanbul / Turkey}
    {\emph{Back-End Developer, Node.JS, AWS}, \emph 
 PHP, Node.JS, MySQL, MongoDB, Redis}
  \entry
    {2020.9 - 2021}
    {Gomeed}
    {Istanbul / Turkey}
    {\emph{Full Stack Web Developer / Project Manager}, \emph 
 PHP, Node.JS, MySQL, MongoDB, Redis}
  \entry
    {2018-2020.8}
    {Kentkart}
    {Kocaeli / Turkey}
    {\emph{Full Stack Web Developer},\emph We are working with More than 10 countries and More than 35 cities around the world and we are developing The Automated Fare Collection, Vehicle Management, Real Time Passenger Information.
I Worked with PHP and Node.js Backend Services, PostgreSQL, MySQL, MongoDB on these projects.}
  \entry
    {2013-2018}
    {Freelance}
    {Turkey / United Kingdom / Italy}
    {\emph{I have developed websites in different sectors in different countries.}}
\end{entrylist}

\section{Open Source Projects}

\begin{entrylist}
  \entry
     {2018}
    {ulak.news}
    {\href{https://github.com/orhanayd/ulak.news}{github.com}}
    {ulak.news is open source project. Get breaking news headlines, news details and search for articles from over 140,000+ (increasing every day.) news our news API. }
  \entry
    {2019}
    {noneDB.org}
    {\href{https://github.com/orhanayd/noneDB}{nonedb.org}}
    {I published in 2019. noneDB is free and open source noSQL database for php projects. No any installations!, Just include and GO.}
  \entry
    {2018}
    {Foreign exchange API}
    {\href{https://github.com/orhanayd/Foreign-exchange-API}{github.com}}
    {Exchange rates API is a free service for current and historical foreign exchange rates
published by the European Central Bank}
  \entry
    {2018}
    {ISBN Search API}
    {\href{https://github.com/orhanayd/isbn-search}{github.com}}
    {ISBN Search API is a free service for retrieve information about book.}
\end{entrylist}

\cleardoublepage

\section{education}

\begin{entrylist}
  \entry
    {2014–2018}
    {Archaeology}
    {Cumhuriyet University / Sivas}
    {Specialization in Protohistoria and Near Eastern Archaeology}
  \entry
    {2013–2014}
    {Web Programming / Computer Operator}
    {Ministry of National Education / Kocaeli}
    {Majoring in Computer Science\\
    Specialization in Web Programming}
\end{entrylist}


\end{document}
